Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/6.Tutorials.tex
Updates to Tutorials section.

\section{Tutorials}\label{chap:tutorial}

Describing here the tutorial app and the example apps that are included either in the repo or in the Kokkos distribution.

>>>>

%\section{Tutorials}\label{chap:tutorial}

The Kokkos programming model distribution includes many examples and benchmark applications as well as tutorial and presentation material. Example applications demonstrate the use of each abstraction as well supported paradigms. Examples cover the use of unified virtual memories on CUDA devices and object polymorphism in Kokkos (virtual functions). The tutorial inclemently introduces the interested reader to Kokkos abstractions and patterns. For the purpose of education each incremental step includes two code version. One code version represents the programming assignment and the other is the solution. The assignment includes instructions and marked code sections that require completion. Benchmark applications provide further insight into performance implications and allows for easy experimentation. Further resources are online. This includes presentation material as well as tutorials on application profiling and the Kokkos Kernels numerical library.
